Computer Science House By-Laws

### 2013-12-17 articles.tex
added some recent amenments, made small changes

% Define the external document to be bylaws for cross referencing purposes
\externaldocument{bylaws}[https://github.com/ComputerScienceHouse/Constitution/blob/master/bylaws.pdf?raw=true]

@@

% % Adding an \asubsubsection -- I feel dirty
\setcounter{secnumdepth}{5}
\newcommand{\asubsubsection}[1]{\paragraph{#1} \label{#1}}
\renewcommand{\theparagraph}{\arabic{section}.\Alph{subsection}.\arabic{subsubsection}.\Alph{paragraph}}

@@

\asection{Active Membership}
\asubsection{Active Membership Qualifications}
Active Membership is open to all students currently enrolled at the Rochester Institute of Technology who have passed the Introductory Evaluation and the most recent Membership Evaluation.
\asubsection{Active Membership Selection}
Qualifying members may self-select into Active Membership by paying dues to the Financial Director and notifying the Evaluations Director.
\\*\\*
Any Alumni Member in bad standing may become an Active Member by notifying the Evaluations Director of their intent to participate, who will bring them up for vote at the next Evaluations meeting. If a majority is in favor of the return, the Alumni is reinstated as an Active Member with Off-Floor status effective immediately. The decision will be announced at the following House meeting.
\asubsection{Active Membership Expectations}
Active members are expected to be active participants in the House as defined in \ref{Expectations of House Members}.
\asubsection{Active Membership Privileges}
Active Members receive the right to:
\begin{itemize}
	\item Vote on all issues brought before the House
	\item Reside on the House
	\item Hold an Executive Board office on the House
	\item Use Computer Science House facilities
	\item Attend Computer Science House functions
	\item Receive priority for available housing on the House when returning from cooperative education
	\item Guaranteed housing in compliance with the Residence Life policies regarding Special Interest Houses and the Housing Selection Process (if they have On-Floor status)
\end{itemize}
\asubsection{Active Membership Evaluations}
Active Members are evaluated semi-annually through the Evaluation Process as described in \ref{Evaluations Processes}.  Failure of the Evaluation Process could result in the member being asked to find alternative housing as soon as possible in accordance with all applicable Residence Life policies regarding room changes.
\asubsection{Active Membership Resignations}
A Active member may resign by submitting in writing the reason for resignation to the Chairman, or Evaluations Director.  The resignation will take effect immediately and an announcement will be made at the following House Meeting.
\asubsection{Active Membership Term}
Active Membership shall last until the member: resigns, fails the Evaluation Process, or changes membership status.

\asection{Alumni Membership}
\asubsection{Alumni Membership Qualifications}
Alumni Membership is open to all former Active members of Computer Science House who passed at least one Membership Evaluation and departed for reasons other than revocation of House Membership.
\asubsection{Alumni Membership Selection}
Alumni who depart house for any reasons other than failure of the Membership Evaluation process, are considered to be in good standing. All other alumni are considered to be in bad standing.
\\*\\*
Active members who depart house prior to the Membership evaluation will be an alumni in bad standing. The member may appeal to EBoard for an exemption based on their circumstances. 
\asubsection{Alumni Membership Expectations}
There are no expectations associated with the Alumni Membership status.
\asubsection{Alumni Membership Privileges}
Alumni Members shall receive the right to:
\begin{itemize}
	\item Use Computer Science House facilities
	\item Attend Computer Science House functions
\end{itemize}
\asubsection{Alumni Membership Evaluations}
Alumni Members are not subject any evaluation.
\asubsection{Alumni Membership Resignations}
There are no resignations associated with Alumni Membership status.
\asubsection{Alumni Membership Term}
Alumni Membership shall last indefinitely or until the member chooses to pursue Active Membership.

@@

\asubsection{Responsibilities of the Evaluations Director}
\begin{enumerate}
	\item To preside over Evaluations Meetings.
	\item To exercise general supervision over Evaluations operations.
	\item To oversee the screening, interviewing, and acceptance or rejection of prospective House members.
	\item To oversee the Semi-Annual Evaluations of current House members.
	\item To collaborate with the Residence Life Advisor to determine room change selection and any changes of membership residency.
	\item To act in collaboration with the Chairman and an additional Executive Board member who is chosen by a simple majority vote among the members of the Executive board as a judicial board for any initial ruling on the interpretation of the House Constitution, House document, or action taken by the House. 
	\item To act as a part of a Judicial Board as defined in \ref{Judicial}.
	\item To prepare the House for Open Houses, tours, and special events.
\end{enumerate}

@@

\asection{Selection}
\asubsection{Dual Directorship}
Social and Research and Development are the only voting Executive Board positions that allow for Dual Directorship. If two candidates elect to run as a Dual Directorship, their names are placed together on a single line of the election ballot. If they are also nominated as a normal directorship or as a dual directorship with another House member, their votes are not cumulative. Each different nomination must be a separate entry on the election ballot. 
Non-voting Executive Board positions (i.e. Ad-Hoc Directors) are not restricted to to single or dual directorship.

@@

	\item Root Type Persons Representative shall be chosen by the current Root Type Persons.

@@

\asection{Number of Votes Required}
The Number of Votes Required refers to the numbers required to achieve a quorum and for a vote to pass. Below are listed four standard votes. Numbers for non-standard votes are defined in the section describing the actual vote.
\asubsection{Simple Majority}
In a Simple Majority Vote, a Quorum is reached if the Total Number of Votes Cast is equal to or exceeds one-half the Total Number of Possible Votes. An option in the vote passes if the number of votes cast for that option is larger than the number of votes cast for every other option individually.
\asubsection{Fifty Percent}
In a Fifty Percent Vote, a Quorum is reached if the Total Number of Votes Cast is equal to or exceeds one-half the Total Number of Possible Votes. An option in the vote passes if the number of votes cast for that option exceeds fifty percent of the Total Number of Votes Cast.
\asubsection{Two-Thirds}
In a Two-thirds Vote, a Quorum is reached if the Total Number of Votes Cast is equal to or exceeds two-thirds the Total Number of Possible Votes. An option in the vote passes if the number of votes cast for the option equals or exceeds two-thirds of the Total Number of Votes Cast.
\asubsection{Three Tiered}
When voting on a set of three choices where each choice can be ranked in a definite order, a selection for either the lowest of highest option will only pass is the votes cast for that selection exceeds fifty percent of the Total Number of Votes Cast. If neither the highest or lowest selection reaches fifty percent, the middle option will then automatically be passed. In a Three-Tiered Vote, a Quorum is reached if the Total Number of Votes Cast is equal to or exceeds two-thirds of the Total Number of Possible Votes.

>>>>

% Define the external document to be bylaws for cross referencing purposes
%\externaldocument{bylaws}[https://github.com/ComputerScienceHouse/Constitution/blob/master/bylaws.pdf?raw=true]
\externaldocument{bylaws}[https://github.com/bencentra/Constitution/blob/master/bylaws.pdf?raw=true]

@@

% Adding an \asubsubsection -- I feel dirty
\setcounter{secnumdepth}{5}
\newcommand{\asubsubsection}[1]{\paragraph{#1} \label{#1}}
\renewcommand{\theparagraph}{\arabic{section}.\Alph{subsection}.\arabic{subsubsection}.\Alph{paragraph}}

@@

\asection{Active Membership}
\asubsection{Active Membership Qualifications}
Active Membership is open to all students currently enrolled at the Rochester Institute of Technology who have passed the Introductory Evaluation and the most recent Membership Evaluation.
\asubsection{Active Membership Selection}
Qualifying members may self-select into Active Membership by paying dues to the Financial Director and notifying the Evaluations Director.
\\*\\*
Any Alumni Member in bad standing (\ref{Alumni Membership Selection}) may become an Active Member by notifying the Evaluations Director of their intent to participate, who will bring them up for vote at the next Evaluations meeting. If a majority is in favor of the return, the Alumni is reinstated as an Active Member with Off-Floor status effective immediately. The decision will be announced at the following House meeting.
\asubsection{Active Membership Expectations}
Active members are expected to be active participants in the House as defined in \ref{Expectations of House Members}.
\asubsection{Active Membership Privileges}
Active Members receive the right to:
\begin{itemize}
	\item Vote on all issues brought before the House
	\item Reside on the House
	\item Hold an Executive Board office on the House
	\item Use Computer Science House facilities
	\item Attend Computer Science House functions
	\item Receive priority for available housing on the House when returning from cooperative education
	\item Guaranteed housing in compliance with the Residence Life policies regarding Special Interest Houses and the Housing Selection Process (if they have On-Floor status)
\end{itemize}
\asubsection{Active Membership Evaluations}
Active Members are evaluated semi-annually through the Evaluation Process as described in \ref{Evaluations Processes}.  Failure of the Evaluation Process could result in the member being asked to find alternative housing as soon as possible in accordance with all applicable Residence Life policies regarding room changes.
\asubsection{Active Membership Resignations}
An Active Member may resign by submitting in writing the reason for resignation to the Chairman, or Evaluations Director.  The resignation will take effect immediately.
\asubsection{Active Membership Term}
Active Membership shall last until the member: resigns, fails the Evaluation Process, or changes membership status.

\asection{Alumni Membership}
\asubsection{Alumni Membership Qualifications}
Alumni Membership is open to all former Active members of Computer Science House who passed at least one Membership Evaluation and departed for reasons other than revocation of House Membership.
\asubsection{Alumni Membership Selection}
Alumni who depart house for any reasons other than failure of the Membership Evaluation process, are considered to be in good standing. All other alumni are considered to be in bad standing.
\\*\\*
Active Members who depart house prior to the Membership evaluation will be an alumni in bad standing. The member may appeal to the Executive Board for an exemption based on their circumstances. 
\asubsection{Alumni Membership Expectations}
There are no expectations associated with the Alumni Membership status.
\asubsection{Alumni Membership Privileges}
Alumni Members shall receive the right to:
\begin{itemize}
	\item Use Computer Science House facilities
	\item Attend Computer Science House functions
\end{itemize}
\asubsection{Alumni Membership Evaluations}
Alumni Members are not subject any evaluation.
\asubsection{Alumni Membership Resignations}
There are no resignations associated with Alumni Membership status.
\asubsection{Alumni Membership Term}
Alumni Membership shall last indefinitely or until the member chooses to pursue Active Membership.

@@

\asubsection{Responsibilities of the Evaluations Director}
\begin{enumerate}
	\item To preside over Evaluations Meetings.
	\item To exercise general supervision over Evaluations operations.
	\item To oversee the screening, interviewing, and acceptance or rejection of prospective House members.
	\item To oversee the Semi-Annual Evaluations of current House members.
	\item To collaborate with the Residence Life Advisor to determine room change selection and any changes of membership residency.
	\item To act as a part of a Judicial Board as defined in \ref{Judicial}.
	\item To prepare the House for Open Houses, tours, and special events.
\end{enumerate}

@@

\asection{Selection}
\asubsection{Dual Directorship}
Social and Research and Development are the only voting Executive Board positions that allow for Dual Directorship. If two candidates elect to run as a Dual Directorship, their names are placed together on a single line of the election ballot. If they are also nominated as a normal directorship or as a dual directorship with another House member, their votes are not cumulative. Each different nomination must be a separate entry on the election ballot. 
Non-voting Executive Board positions (i.e. Ad-Hoc Directors) are not restricted to single or dual directorship.

@@

	\item A candidate for the Operational Communications Directorship shall be chosen by the current Root Type Persons.
	\item The candidate is given a minimum of twenty-four hours to accept or decline the nomination.
	\item The candidate is presented to the Executive Board for approval. This Executive Board meeting is closed to the Executive Board Members, Root Type Persons, and House members with explicit invitation from the Executive Board.
	\item All current Executive Board Voting Members must be present during the discussion and voting period unless that member is a candidate for the position, in which case the member is absent and their vote is abstained. A simple majority Executive Board vote, as described in \ref{Simple Majority}, is taken to determine whether the candidate is selected for the position.

@@

\asection{Number of Votes Required}
The Number of Votes Required refers to the numbers required to achieve a quorum and for a vote to pass. Below are listed four standard votes. Numbers for non-standard votes are defined in the section describing the actual vote.
\asubsection{Simple Majority}
In a Simple Majority Vote, a Quorum is reached if the Total Number of Votes Cast is equal to or exceeds one-half the Total Number of Possible Votes. An option in the vote passes if the number of votes cast for that option is larger than the number of votes cast for every other option individually.
\asubsection{Fifty Percent}
In a Fifty Percent Vote, a Quorum is reached if the Total Number of Votes Cast is equal to or exceeds one-half the Total Number of Possible Votes. An option in the vote passes if the number of votes cast for that option exceeds fifty percent of the Total Number of Votes Cast.
\asubsection{Two-Thirds}
In a Two-thirds Vote, a Quorum is reached if the Total Number of Votes Cast is equal to or exceeds two-thirds the Total Number of Possible Votes. An option in the vote passes if the number of votes cast for the option equals or exceeds two-thirds of the Total Number of Votes Cast.
\asubsection{Three Tiered}
When voting on a set of three choices where each choice can be ranked in a definite order, a selection for either the lowest or highest option will only pass if the votes cast for that selection exceed fifty percent of the Total Number of Votes Cast. If neither the highest or lowest selection exceeds fifty percent, the middle option will then automatically be passed. In a Three-Tiered Vote, a Quorum is reached if the Total Number of Votes Cast is equal to or exceeds two-thirds of the Total Number of Possible Votes.

### 2013-12-17 bylaws.tex
added some recent amenments, made small changes

% Define the external document to be constitution for cross referencing purposes
\externaldocument{constitution}[https://github.com/ComputerScienceHouse/Constitution/blob/master/constitution.pdf?raw=true]

@@

% Headings
\pagestyle{myheadings}
\markright{{\rm CSH Constitution \hfill \datechanged \hfill Page }}
% Reference example:
%Test reference \ref{House Objectives} House Objectives.

@@

% BY-LAW II - GENERAL OPERATIONS OF THE HOUSE
\bylaw{General Operations of the House}
\bsection{Standard Operating Session}
The Standard Operating Session for Computer Science House is during the fifteen weeks of Fall and Spring semesters. The Summer Sessions, Intersessions, Institute breaks, and all end of Semester Exam Weeks are considered non-standard operating sessions. Unless explicitly stated otherwise, the requirements and expectations deﬁned in the constitution are for the Standard Operating Session.

>>>>

% Define the external document to be constitution for cross referencing purposes
%\externaldocument{constitution}[https://github.com/ComputerScienceHouse/Constitution/blob/master/constitution.pdf?raw=true]
\externaldocument{constitution}[https://github.com/bencentra/Constitution/blob/master/articles.pdf?raw=true]

@@

% Headings
\pagestyle{myheadings}
\markright{{\rm CSH Constitution \hfill \datechanged \hfill Page }}

% Reference example:
%Test reference \ref{House Objectives} House Objectives.

@@

% BY-LAW II - GENERAL OPERATIONS OF THE HOUSE
\bylaw{General Operations of the House}
\bsection{Standard Operating Session}
The Standard Operating Session for Computer Science House is during the thirty weeks of Fall and Spring semesters. The Summer Sessions, Intersessions, Institute breaks, and all end of Semester Exam Weeks are considered non-standard operating sessions. Unless explicitly stated otherwise, the requirements and expectations deﬁned in the constitution are for the Standard Operating Session.
